Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-20 analysis/paper/paper.Rmd
Add section on data cleaning

>>>>

## Data Cleaning

Efforts were made to standardise the scoring as much as possible.
In some cases the `software_avail`, or the openness of the software used, score did not agree with the software that was recorded and these scores were modified after discussion to match the agreed on ratings.
For example, a paper was rated as having a `software_avail` rating of `3`, but the evaulator noted that Excel had been used.
Here, the `software_avail` rating was changed to `2` to bring it into line with the agreed upon guidelines.
In other cases, papers did not adequately describe all the software used, e.g., GenAlEx, an Excel add-on, was referred to but Excel was not mentioned in the text.
In these cases, Excel was added to the `software_used` column.
